\bibitem[1]{1}
{ Adriana M. Rojas Mora} (2009).
 {\em The Use of Quantitative Modelling in the Directors \& Officers (D\&O) Liability Insurance Market\/}. Master thesis. Georgia State University.

\bibitem[2]{2}
{ Blakeley B. McShane} (2012).
Predicting Securities Fraud Settlements and Amounts: A Hierarchical Bayesian Model of Federal Securities Class Action Lawsuits. {\em Journal of Empirical Legal Studies\/}, \,{\bf 9}(3), pp.\,482-510.

\bibitem[3]{3}
{ Alexander Aganin}. (2017).
Securities Class Action Filings. {\em Cornerstone Research  \/}. 31 Jan. pp.\,2-9.

\bibitem[4]{4}
{ Laarni T. Bulan}. (2017).
Securities Class Action Settlements. {\em Cornerstone Research and the Stanford Law School Securities Class Action Clearinghouse \/}. 15 Mar. pp.\,1-20.

\bibitem[5]{5}
{ Google News} (2011). {\em Google, Inc\/}. Available at  \href{https://news.google.com/news/headlines?ned=uk&hl=en-GB}{\colorbox{Graylight}{<http://news.google.com>.}}

\bibitem[6]{6}
{ Yahoo! Finance}. (2011). {\em Yahoo, Inc\/}. Available at \href{https://finance.yahoo.com/lookup}{\colorbox{Graylight}{<http://finance.yahoo.com>.}}

\bibitem[7]{7}
{The Pennsylvania State University (Producer)}. (2017).
{\em STAT 510: Applied Time Series Analysis\/}. Retrieved from \href{https://onlinecourses.science.psu.edu/stat510/node/33}{\colorbox{Graylight}{<https://onlinecourses.science.psu.edu>.}}

\bibitem[8]{8}
{The Pennsylvania State University (Producer)}. (2017).
{\em STAT 897D: Applied Data Mining and Statistical Learning\/}. Retrieved from \href{https://onlinecourses.science.psu.edu/stat510/node/33}{\colorbox{Graylight}{<https://onlinecourses.science.psu.edu>.}}

\bibitem[9]{9}
{Jason Brownlee}. (2017).
{\em Introduction to Time Series Forecasting With Python: Discover How to Prepare Data and Develop Models to Predict the Future\/}[Online]. [Accessed 8 August 2017]. Unpublished paper available from: \href{https://s3.amazonaws.com/MLMastery/time_series_forecasting_with_python_sample.pdf}{\colorbox{Graylight}{<https://s3.amazonaws.com/MLMastery>.}}

\bibitem[10]{10}
{Jason Brownlee}. (2017).
{\em Master Machine Learning Algorithms: Discover How They Work and Implement Them From Scratch\/}[Online]. [Accessed 8 August 2017]. Unpublished paper available from: \href{https://s3.amazonaws.com/MLMastery/master_machine_learning_algorithms_sample.pdf}{\colorbox{Graylight}{<https://s3.amazonaws.com/MLMastery>.}}

\bibitem[11]{11}
{ Tom Baker and Sean J. Griffith} (2007).
Predicting corporate governance risk: evidence from the directors and officers liability insurance market.  {\em The University of Chicago Law Review/}, \,{\bf 74}, pp.\,487-544.

\bibitem[12]{12}
{ Brian T. Fitzpatrick} (2010).
An Empirical Study of Class Action Settlements and Their Fee Awards. {\em  Journal of Empirical Legal Studies\/}. {\bf 7}(4), pp.\,811-846.

\bibitem[13]{13}
{ Stephen J. Choi} (2004).
The Evidence on Securities Class Actions. {\em Vanderbilt Law Rev\/}. {\bf 56}(6), pp.\,1465-1535.

\bibitem[14]{14}
{ Bryan Arguello} (2015).
 {\em A Survey of Feature Selection Methods: Algorithms and Software\/}. Master thesis. The University of Texas at Austin.
 
\bibitem[15]{15}
{ Gavin Hackeling} (2014).
{\em Mastering Machine Learning with scikit-learn\/}. 2nd ed. Birmingham: Packt Publishing.

\bibitem[16]{16}
{ Tom Baker and Sean J. Griffith} (2007).
Predicting Corporate Governance Risk: Evidence from the Directors' \& Officers' Liability Insurance Market. {\em University of Chicago Law Review\/}, {\bf 74}(2), pp.\, 487-499.

\bibitem[17]{17}
{Jeff Leek} (2015).
 {\em The Elements of Data Analytic Style: A guide for people who want to analyse data\/}[Online]. London: Simplystats. [Accessed 8 August 2017]. Available from: \href{http://worldpece.org/sites/default/files/datastyle.pdf}{\colorbox{Graylight}{<http://worldpece.org/sites/default/files/datastyle.pdf>.}}
 
 \bibitem[18]{18}
{Johns Hopkins} (2014).
 {\em Practical Machine Learning\/}[Online]. London: Simplystats. [Accessed 20 August 2017]. Available from: \href{https://www.coursera.org/learn/practical-machine-learning#syllabus}{\colorbox{Graylight}{<https://www.coursera.org/learn/practical-machine-learning>.}}
 
 \bibitem[19]{19}
{Sebastian Raschka} (2016). sebastianraschka 11 June.
 {\em Model evaluation, model selection, and algorithm selection in machine learning\/}[Online]. [Accessed 10 August 2017]. Available from: \href{https://sebastianraschka.com/blog/2016/model-evaluation-selection-part1.html}{\colorbox{Graylight}{<https://sebastianraschka.com/blog/2016/model-evaluation-selection>.}}


